\section{\bfseries System Architecture}
\Large
The system architecture section explains the technical design of the app, structured using the MVVM (Model-View-ViewModel) pattern, which ensures maintainability, testability, and modularity.

\subsection{Model}
The app utilizes the MVVM architecture, which is advantageous due to its:
\begin{itemize}
    \item \textbf{Maintainability}: Easy to update and version the app.
    \item \textbf{Extensibility}: Easy to refactor or add new functionality without significantly altering the codebase.
    \item \textbf{Testability}: Facilitates writing unit tests for each layer.
    \item \textbf{Transparent Communication}: The ViewModel connects the View and Model layers instead of having a direct connection.
\end{itemize}

\subsection{System Architecture Layers}

\subsubsection{View Layer}
\textbf{Components}: UI components, such as Views, Activities, and Fragments, which interact with the ViewModel to observe data changes and update the user interface.

\textbf{Responsibilities}:
\begin{itemize}
    \item Display tracking data, including running time, location, distance, and steps.
    \item Respond to user inputs like start, pause, resume, and stop actions.
    \item Continuously update data displayed on the screen in real time.
\end{itemize}

\subsubsection{ViewModel Layer}
\textbf{Components}: ViewModel classes, LiveData, and StateFlow.

\textbf{Responsibilities}:
\begin{itemize}
    \item Connect the View layer with the Model layer, ensuring consistent and up-to-date data for the UI.
    \item Manage and update data from the Model layer.
    \item Handle user inputs and update the UI state (e.g., when a run is started, paused, or resumed).
\end{itemize}

\subsubsection{Model Layer}

\textbf{Components}: Repositories and local data sources.

\textbf{Responsibilities}:
\begin{itemize}
    \item Gather and manage data from local sources.
    \item \textbf{Local Storage}: Store and retrieve user information, such as run statistics, user profiles, and activity data.
    \item \textbf{Data Transformation}: Process raw data (e.g., GPS coordinates) and transform it into usable information (e.g., calculate distance).
\end{itemize}

\subsection{Diagram}
A diagram illustrating the MVVM architecture, showing the flow of data between the View, ViewModel, and Model layers.


